%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD Student} % Job title
    {INRIA} % Organization
    {Sophia Antipolis, France} % Location
    {Feb. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Proposed, implemented and validated several methods for action recognition (multimodal RBG+D desriptor, Brownian Covariance, Spatio-Temporal layout for Fisher Vector) and action detection (Real time Fisher Vector representation), }
        \item {Published 9 scientific papers~\cite{Crispim:2017, Das:2017, koperski:2016, Crispim:2016, Negin:2016, Negin:2015, ortiz:2015, Bilinski:2014, koperski:2014} and~\cite{koperskiphd:2017}}
        \item {The code of the proposed methods was successfully transferred to Toyota.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Internship} % Job title
    {Disney Research} % Organization
    {Pittsburgh, PA, USA} % Location
    {Jan. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supervisors: Peter Carr, Slawomir Bak,}
        \item {Proposed cross-view Fisher Vector representation for People Re-Identification,}
        \item {Published 1 scientific paper~\cite{koperski:2017}
,}
        \item {1 patent request was filed.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Internship} % Job title
    {INRIA} % Organization
    {Sophia Antipolis, France} % Location
    {Apr. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supervisor: Francois Bremond,}
        \item {Proposed multimodal RGB-D descriptor for action recognition,}
        \item {Published 1 scientific paper~\cite{koperski:2014}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {Wroclaw University of Technology} % Organization
    {Wroclaw, Poland} % Location
    {Apr. 2012 - Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Teaching "Algorithms and Data Structures"}
      	\item {Teaching "Operating Systems"}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Engineer} % Job title
    {Poznan University of Technology} % Organization
    {Poznan, Poland} % Location
    {Jan. 2010 - Apr. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {BirdWatch project at Intelligent Decision Support System Laboratory,}
        \item {Implemented and validated bird species detection system for mobile devices (ARM), }
      	\item {Teaching "Software Engineering"}
        \item {Published 1 book chapter~\cite{kirchner:2011}.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
